---
title: "Module 8-Final_Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading the required libraried and data from 2 different sources

```{r }
setwd("D://Data Analytics")
library(caret);library(rattle); library(rpart)
```


```{r Loading data}
OriTrain <- read.csv("pml-training.csv")
OriTest <- read.csv("pml-testing.csv")
dim(OriTrain);dim(OriTest)
```
 Looking at the train data
```{r glance at train data}
str(OriTrain)
```
 If the column data is less than 70% it is diffcult to impute. So we are looking the columns which are having more than 70% nulls

``` {r Remove columns if contains more than 70% nulls}
NullColumns <- which(colSums(is.na(OriTrain) |OriTrain=="")>0.7*dim(OriTrain)[1]) 
OriTrain<- OriTrain[,-NullColumns]
```
Removing 7 variables as we do not need that information 
```{r removing unneccessary variables}
OriTrain <- OriTrain[,-c(1:7)]
## Data After removing nulls and non-important columns
dim(OriTrain)
```


To check the efficiancy of the model, we are splitting the training data into train and test before implementing on actual test data

```{r Splitting train data into train and test data}
set.seed(12345)
inTrain <- createDataPartition(OriTrain$classe, p=0.75, list=FALSE)
train <- OriTrain[inTrain,]
test <- OriTrain[-inTrain,]
dim(train); dim(test)
```
We will check the accuracy by applying multiple models. Below is Classification Model

```{r Applying Classification model}

tcontrol <- trainControl(method="cv", number=5)
CTModel <- train(classe~., data=train, method="rpart", trControl=tcontrol)
fancyRpartPlot(CTModel$finalModel)
```

Prdiction of Test data using Cross-Validation Model

```{r prediction for test data using CV model}
pred <- predict(CTModel,newdata=test)
confMat <- confusionMatrix(test$classe,pred)
confMat$table; confMat$overall[1]

```

Random Forest Model prediction using Train data

```{r Predicting with Random Forests}
control1 <- trainControl(method="cv", number=5)
Model1 <- train(classe~., data=train, method="rf", trControl=control1, verbose=FALSE)

print(Model1)

```
Test data model prediction


```{r test prediction}
pred <- predict(Model1,newdata=test)

confMat1 <- confusionMatrix(test$classe,pred)
confMat1$overall[1];Model1$finalModel$classes

```
Gradient Boosting model

```{r Prediction with Gradient Boosting}
control1 <- trainControl(method="cv", number=5)
Model2 <- train(classe~., data=train, method="gbm", trControl=control1, verbose=FALSE)
print(Model2)

```

```{r test prediction with Gradient Boosting}
pred <- predict(Model2,newdata=test)

confMat2 <- confusionMatrix(test$classe,pred)
confMat2$table
print(confMat2)

```
Applying better model 

```{r Applying Final model on original test data}

OriTestpred <- predict(Model1, newdata=OriTest)
OriTestpred

```