---
title: "Week4Assignment"
author: "laxmi"
date: "07/08/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview


Week 4 Assignment to Develop Data Products. This app is dynamic line chart based on what is selected

The project includes: Radio button 



## Application Contains

Form of Input used: Radio Button

Reactive output Line chart displayed based on the selections

The server.R and ui.R codes are posted on github at:https://github.com/laxmigvcs/test-repo/blob/gh-pages/ui.R
https://github.com/laxmigvcs/test-repo/blob/gh-pages/server.R

This app is hosted at: https://laxmigvcs.shinyapps.io/week4assignment/

## Shiny Code

library(plotly)
library(shiny)

shinyUI(fluidPage(
    
    radioButtons('variable', 'choose selection', choices = c('hp','disp'), selected = 'hp',
                 inline = FALSE, width = NULL, choiceNames = NULL,
                 choiceValues = NULL)
    ,plotlyOutput("plot1")
))


library(shiny)
library(plotly)

shinyServer(function(input, output) {
    
    output$plot1 <- renderPlotly({
        
        if (input$variable == 'hp') {
            
            plot_ly(mtcars, x= ~wt, y = ~hp,type = "scatter", mode = "lines+markers", color = ~as.factor(cyl))
        }
        
        else {
            plot_ly(mtcars, x= ~wt, y = ~disp,type = "scatter", mode = "lines+markers", color = ~as.factor(cyl))  
        }
        
    })
    
})



## output

``` {r}
library(plotly)
plot_ly(mtcars, x= ~wt, y = ~hp,type = "scatter", mode = "lines+markers", color = ~as.factor(cyl))
```





